### 2016-10-25 paper/evaluation.tex
initial par on RQ2

\Fix{Explain scatter plot}

\begin{figure}[h!]%
    \centering
    \manpage{}
    \subfigure[\Fix{normal}]{
        \includegraphics[width=0.3\textwidth]{results/rq1/plots/scatterplot-norm.pdf}
    }
    \\
    \subfigure[\Fix{long}]{
        \includegraphics[width=0.3\textwidth]{results/rq1/plots/scatterplot-long.pdf}
    }\\
    \subfigure[\Fix{vlong}]{
        \includegraphics[width=0.3\textwidth]{results/rq1/plots/scatterplot-vlong.pdf}
    }
    \\
    \caption{\Fix{...}}
\end{figure}

@@

>>>>

We compared the execution time and number of tests for each subject. \Fix{...}

\begin{figure}[h!]%
    \centering
    \begin{minipage}{4.5in}%
        \subfigure[\Fix{normal}]{
            \includegraphics[width=0.3\textwidth]{results/rq1/plots/scatterplot-norm.pdf}
        }%
        \subfigure[\Fix{long}]{
            \includegraphics[width=0.3\textwidth]{results/rq1/plots/scatterplot-long.pdf}
        }\\
        \subfigure[\Fix{vlong}]{
            \includegraphics[width=0.3\textwidth]{results/rq1/plots/scatterplot-vlong.pdf}
        }%
    \end{minipage}
    \caption{\Fix{...}}
\end{figure}

@@

To evaluate the distribution of CPU and IO bound in regression tests
from the sample set, we proposed the definition of \emph{cpuness}
computed as the follow: $((user\_t + system\_t) / elapsed\_t) * 100$,
where \emph{user\_t} is the elapsed time of execution in \emph{user
mode}, \emph{system\_t} is the elapsed in \emph{kernel mode}, and
\emph{elapsed\_t} is the elapsed time to finish the execution. We
measured the \emph{cpuness} of each regression test \Fix{...elaborate
the meaning of cpuness} \Fix{Describe how I measured user, system and
"wall" time}.  \Fix{Explain results}.  \Fix{show plots}
